\sffamily \Large {\bfseries Introspection dynamics in asymmetric multiplayers games}

### 2023-03-01 latex/article.tex
Marta stuff added. Ready to be printed to review between us

\begin{document}
\maketitle
\onehalfspacing
\section*{Abstract}

% 150 to 250 words
% 4 to 6 keywords: multiplayer games, asymmetric games, non-linear interactions, learning model, introspection dynamics, strategy abundance

%-----SP ABSTRACT-----%
Evolutionary game theory and learning models have contributed to the understanding of social interactions and how individuals may learn to act strategically.
The simplest models involve two identical players. However, many interactions in everyday life are often complex, occurring among more than two individuals that differ between themselves. Such interactions can be captured by asymmetric multiplayer games. 
Recently, introspection dynamics has proven to be a useful learning model for tackling asymmetric games. In this dynamics, at each time step, players compare their current strategy to an alternative strategy. If the update results in a payoff advantage, the new strategy is more likely adopted. This model provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (i.e., the stationary distribution). 
In this paper, we extend some of the previous results of introspection dynamics on 2-player asymmetric games to games with multiple players. First, we derive a general explicit formula that allows us to numerically compute the stationary distribution of any multiplayer asymmetric game. Second, we obtain analytical expressions of the stationary distribution for two special cases, i) additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and ii) symmetric multiplayer games with two strategies. Finally, we revisit several classical games like the general public goods game to illustrate our results.

@@

\begin{comment}
The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves. This case, in turn, can be captured by a multiplayer asymmetric game. The complexity of these games increases both with the number and diversity of players.
From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
Introspection dynamics has proven to be a useful learning model to tackle complex games.
%To analyse more complex games, researchers typically use approximations, e.g. weak selection, small mutation. 
Here, our aim is to analyse multiplayer and (a)symmetric games. We extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
We divide games into two main categories: additive and non-additive (or general) games.
In additive games, for any player, the difference between the payoffs provided by any two actions (or strategies) is constant, regardless of the co-players' actions. 
Non-additive are all games that do not hold this property; hence, general games.
For additive games, we derive the stationary distribution of strategies analytically, for any number of players and strategies. 
%Additionally, we find that the joint distribution of strategies factorizes over the marginal distribution of strategies.
Additionally, we find that the frequency of a state (a combination of actions played by each player) corresponds to the product of the frequencies of each player playing their respective strategy.
For non-additive games, we obtain the analytical stationary distribution for 2-strategies symmetric games. For other cases, we provide numerical results. 
To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
%add rewarding game
\end{comment}
\newpage

@@

The simplest form of social interaction occurs between two individuals. These pairwise interactions have been studied extensively \cite{Hofbauer:book:1998}. Despite their simplicity, they provide important insights, e.g., on how social species can maintain cooperation \cite{Axelrod:book:1984, Nowak:book:2011}. An ubiquitous example of a model game for two players is the prisoner's dilemma. Here, the two individuals have a temptation to cheat, but at the same time, players are better off if they help each other. Solving this paradox has been the focus of many studies. These studies provide several explanations for why one can expect cooperation in such interactions \cite{Nowak:Science:2006}. 
%some references
% non-linearity
\noindent Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
Importantly, most of these situations cannot be captured by the sum of several pairwise interactions. Thus, to account for such non-linearities, we need to consider multiplayer games \cite{Gokhale:DGAA:2014}. One well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}. A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators). However, most forms of sanctioning are considerably costly \cite{Henrich:Science:2006}. Therefore, an additional (second-order) dilemma is at stake: deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do. As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma. However, this tempts everyone to not engage in costly punishment (or rewarding). Cooperation can break down when there are not enough individuals punishing (or giving rewards). For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.

@@

Another interesting effect that can be explored with multiplayer games is the scale or size of the interaction itself. In situations that require some sort of coordination and where expectations on others play an important role in one's decisions, a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}. Likewise, it has been shown that it is hard to cooperate in large groups for some conditions \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
This is not a general effect, though. It can happen that adding more players actually promotes cooperation. In \cite{gokhale:JTB:2011}, authors investigate the 2-player and 3-player cases of a task allocation problem. Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in freeloading.

@@

Additionally, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.

@@

\noindent Complexity further increases when players differ significantly among themselves. This diversity can be captured by asymmetric games \cite{Taylor:JAP:1979, Schuster:AB:1981, Gaunersdorfer:TPB:1991, Hofbauer:JMB:1996, Hofbauer:GEB:2005, Ohtsuki:JTB:2010, McAvoy:PlosCB:2015, Veller:JET:2016, Hauser:Nature:2019}. In symmetric games, all players are indistinguishable. Thus, to fully characterise the state of the game, we only require to know the number of players playing each strategy. Conversely, in asymmetric games, players can be different in several ways. For example, players can have different types or roles, which can have consequences in the payoffs and strategies. Therefore, they can have uneven effects on others' payoffs too. For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022}. Hence, to fully describe the state of the game, we need to know which of the players is doing what. This greatly increases the size of the game's state space; even more so, for more than two players.  \\ \\ 

@@

\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different. Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games. As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}. In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer games and asymmetric games.%, pointing out the gaps.

%possibly new section \section*{Background} but then where to put "proposal"?

\section*{Related Work}

@@

% deterministic EGT
From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior. 
In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time. More successful strategies tend to persist in the population, either by genetic or cultural inheritance. The first key concept in evolutionary game theory is ``evolutionary stable strategy" (ESS),  introduced in 1973, in the seminal paper of John Maynard Smith and George Price \cite{Maynard-Smith:Nature:1973}. A (monomorphic) population playing an ESS cannot be invaded by mutants. The concept of ESS, originally proposed for parwise encounters, was already extended for multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}. Although suggestive of an evolutionary process, ESS does not really describe a dynamical system. In the more classical infinite population models (deterministic EGT), ordinary differential equations are the central mathematical tools \cite{Hofbauer:book:1998}. Among these the replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} is the most popular model. Replicator equation has been widely used and easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}. More recently, also the replicator-mutator equation was applied to study the dynamics of multiplayer games \cite{Duong:DGAA:2020}. As for asymmetric games, a few additional assumptions are needed. For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Gokhale:PRSB:2012, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}. For role games, a strategy must include the action played in each of the two roles. The case of asymmetric games with more than two players is substantially less studied within deterministic EGT. Exceptions are  \cite{Gokhale:PRSB:2012, Zhang:arxiv:2022}. Notably, although these works study multiplayer games, they consider, at most, two different types (drawn from two populations), which leaves out the exploration of full asymmetry.
% models of multiple populations seem unnatural
% stochastic EGT
\noindent To account for stochastic effects that are naturally present in finite populations, another set of tools was developed, known as stochastic evolutionary game dynamics.  \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009}. Besides the finiteness of population sizes, it also considers random mutations. Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}. 
%When deriving fixation probabilities and times, it is assumed that mutations are rare, such that, no new mutant arises between the very first and its eventual fixation \cite{}. 
%\cite{Chalub:BMB:2019}
These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived. Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}. For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\ 
%comment on the pervasiveness of weak selection
%strategy abundance papers (intermediate mutation or mutation-selection equilibrium)
%2-player symmetric and asymmetric games, any number of strategies, Birth-death process \cite{ohtsuki:JTB:2010}
%2-player symmetric and asymmetric games, any number of strategies, Death-birth process \cite{Sekiguchi:PA:2013}

@@

%[Learning models] IM NOT VERY HAPPY WITH HOW THIS SECTION READS YET
%learning models in general
\noindent Different from evolutionary game theory, learning models (of strategic behavior) take another approach \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}. There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically. 
Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}. 
\noindent Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}. The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made. Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{Fudenberg:book:1998b}. In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
\\  \\
%learning models for asymmetric and multiplayer games? fictious play for multiplayer games \cite{fudenberg:book:1998b} 
%can we say most of learning models have no analytical or exact results?
%quantal response equilibrium
%introspection dynamics
\noindent Introspection dynamics has proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}. 
This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round. We discuss the model formally in the next section. 
While in Couto et al. \cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players. Indeed, as each player assumes that all others remain the same when doing the counterfactual comparison, introspection dynamics is an appropriate model to deal with the complexity introduced by multiple players. Particularly, it allows a natural exploration of full asymmetry in many-player games, compared to population models.
\\ \\
%[Our proposal]
\noindent Here, we extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
For general games, we obtain the analytical stationary distribution for 2-strategy symmetric games.
For a particularly simple class of games -- additive games -- we derive the stationary distribution of strategies analytically, for any number of players and strategies, and with no restriction to symmetric games. 
To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games. Finally, we also study the asymmetric version of a public goods game with a rewarding stage \cite{Pal:NatCom:2022}.

@@

\label{Th:additive-games-stationary-dist}
\end{Prop}
\noindent For a proof of the Propositions and Corollaries, please see Appendix. Using the stationary distribution, one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distribution) using Eq. (\ref{Eq:marginal-definition}). In this regard, introspection learning in additive games is particularly interesting. The stationary distribution and the marginal distributions of introspection dynamics in additive games are related in a special way,

@@

\noindent where the marginal probability, $\xi_{j,a_j}$, is the cumulative probability that player $j$ plays $a_j$ at the stationary distribution. For the $N$-player additive game, this is given by,

@@

We also study introspection dynamics in this game with asymmetric players. We use the same setup that we used for studying the asymmetric linear public goods. The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2. In Supplementary Figure 1, we study two cases, first in which the public good is synergistic ($w > 1$, and players have a high average cost) and second in which public good is discounted (and players have a lower average cost). In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit. The only noticebale difference between the two cases is the minimum relationship between the asymmetries $\delta_b$ and $\delta_c$ that results in high cooperation for the player with low cost and high benefit. When we observe individual cooperation frequency versus the synergy/discount factor, $w$ (Supplementary Figure 2), we find that when players are symmetric with respect to just benefits (or just costs), the one with the lowest cost (or highest benefit) cooperates with a high probability across all types of public goods, even for a high value of average cost.

>>>>

\begin{document}
\maketitle
\onehalfspacing
\section*{Abstract}
\section*{Abstract}

% 150 to 250 words

Evolutionary game theory and models of learning provide a powerful framework to describe strategic decision-making in social interactions. 
In the simplest case, these models describe games among two identical players. 
However, many interactions in everyday life are more complex. 
They involve more than two players who may differ in their available actions and in their incentives to choose each action. 
Such interactions can be captured by asymmetric multiplayer games. 
Recently, introspection dynamics has been introduced to explore such asymmetric games. 
According to this dynamics, at each time step players compare their current strategy to an alternative strategy. 
If the alternative strategy results in a payoff advantage, it is more likely adopted. 
This model provides a simple way to compute the players’ long-run probability of adopting each of their strategies. 
In this paper, we extend some of the previous results of introspection dynamics for 2-player asymmetric games to games with arbitrarily many players. 
First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
Second, we obtain explicit expressions of the stationary distribution for two special cases. These cases are additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and symmetric multiplayer games with two strategies. 
To illustrate our results, we revisit several classical games such as the public goods game.\\

% 4 to 6 keywords: multiplayer games, asymmetric games, non-linear interactions, learning model, introspection dynamics, strategy abundance, aditive games

\noindent \textbf{Keywords}: multiplayer games, asymmetric games, non-linear interactions, introspection dynamics, strategy abundance, additive games.

%Evolutionary game theory and learning models have contributed to the understanding of social interactions and how individuals learn to act strategically.
%The simplest models involve two identical players. However, many interactions in everyday life are often complex, occurring among more than two individuals that differ between themselves. Such interactions can be captured by asymmetric multiplayer games. 
%Recently, introspection dynamics has proven to be a useful learning model for tackling asymmetric games. In this dynamics, at each time step, players compare their current strategy to an alternative strategy. If the update results in a payoff advantage, the new strategy is more likely adopted. This model provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (i.e., the stationary distribution). 
%In this paper, we extend some of the previous results of introspection dynamics on 2-player asymmetric games to games with multiple players. First, we derive a general explicit formula that allows us to numerically compute the stationary distribution of any multiplayer asymmetric game. Second, we obtain analytical expressions of the stationary distribution for two special cases, i) additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and ii) symmetric multiplayer games with two strategies. Finally, we revisit several classical games like the general public goods game to illustrate our results.
%%word count: 236

%-----SP ABSTRACT-----%
%Social interactions are often modelled using simultaneous games. The simplest model involves two identical players. However, interactions in everyday life are complex and often involve more than two individuals that differ between themselves. Such interactions can be captured more realistically using asymmetric multiplayer games. Over the years, learning models and models from evolutionary game theory have studied how players may learn to play strategically in these games. Recently, introspection dynamics has proven to be a useful learning model for tackling complex games. In this dynamics, players compare their current strategy to an alternative strategy. If the update results in a payoff advantage, it is more likely adopted. This dynamics provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (the stationary distribution). In this paper, we extend some of the previous analytical results of introspection dynamics on games with two-players to games with more players. We obtain analytical expressions of the stationary distribution for multiplayer asymmetric games that have the special property of being additive in the payoffs. In such games, the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions that their co-players play. In addition, we derive the stationary distribution for symmetric multiplayer games with two strategies. We discuss several classical games like the general public goods game to illustrate our results.

@@

\begin{comment}
The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves. This case, in turn, can be captured by a multiplayer asymmetric game. The complexity of these games increases both with the number and diversity of players.
From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
Introspection dynamics has proven to be a useful learning model to tackle complex games.
%To analyse more complex games, researchers typically use approximations, e.g. weak selection, small mutation. 
Here, our aim is to analyse multiplayer and (a)symmetric games. We extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
We divide games into two main categories: additive and non-additive (or general) games.
In additive games, for any player, the difference between the payoffs provided by any two actions (or strategies) is constant, regardless of the co-players' actions. 
Non-additive are all games that do not hold this property; hence, general games.
For additive games, we derive the stationary distribution of strategies analytically, for any number of players and strategies. 
%Additionally, we find that the joint distribution of strategies factorizes over the marginal distribution of strategies.
Additionally, we find that the frequency of a state (a combination of actions played by each player) corresponds to the product of the frequencies of each player playing their respective strategy.
For non-additive games, we obtain the analytical stationary distribution for 2-strategies symmetric games. For other cases, we provide numerical results. 
To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
%add rewarding game
\end{comment}

@@

Social behavior has been studied extensively through pairwise interactions \cite{Hofbauer:book:1998}. Despite their simplicity, they provide important insights, such as how populations can sustain cooperation \cite{Axelrod:book:1984, Nowak:Science:2006,  Nowak:book:2011}. 
%An ubiquitous example of a model game for two players is the prisoner's dilemma. Here, the two individuals have a temptation to cheat, but at the same time, players are better off if they help each other. Solving this paradox has been the focus of many studies. These studies provide several explanations for why one can expect cooperation in such interactions \cite{Nowak:Science:2006}. 
Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
Most of these situations cannot be captured by the sum of several pairwise interactions. Thus, to account for such non-linearities, one needs to consider multiplayer games \cite{Gokhale:DGAA:2014}. A well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}. A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators). However, most forms of sanctioning are considerably costly \cite{Henrich:Science:2006}. Therefore, an additional (second-order) dilemma is at stake: deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do. As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma. As such, this tempts everyone not to engage in costly punishment (or rewarding), and cooperation can break down. For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.

@@

Another interesting effect that can be explored with multiplayer games is the scale or size of the interaction itself. In situations that require some sort of coordination and where expectations on others play an important role in one's decisions, a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}. Likewise, it has been shown that it is hard to cooperate in large groups \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
This is not a general effect, though. It can happen that adding more players actually promotes cooperation. Gokhale and Traulsen (2011) investigate the 2-player and 3-player cases of a task allocation problem \cite{gokhale:JTB:2011}. Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in free-riding.

@@

Additionally, interaction group size can vary in a population of players. There, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.

@@

\noindent Complexity further increases when players differ significantly among themselves. This diversity can be captured by asymmetric games \cite{Taylor:JAP:1979, Schuster:AB:1981, Gaunersdorfer:TPB:1991, Hofbauer:JMB:1996, Hofbauer:GEB:2005, Ohtsuki:JTB:2010, McAvoy:PlosCB:2015, Veller:JET:2016, Hauser:Nature:2019}. In symmetric games, all players are indistinguishable. Thus, to fully characterise the state of the game, we only require to know the number of players playing each strategy. Conversely, in asymmetric games, players can differ in their available actions and in their incentives to choose each action; players are of different types or roles. Therefore, they can have uneven effects on others' payoffs too. For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022, Wang:PTRSB:2023}. Hence, to fully describe the state of the game, we need to know which of the players is doing what. This greatly increases the size of the game's state space; even more so, for more than two players.  \\ \\ 

@@

%\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different. Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games. As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}. In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer games and asymmetric games.

%\section*{Related Work}

@@

% deterministic EGT
\noindent From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior. %, in particular, in multiplayer and asymmetric games.
%In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time. More successful strategies tend to persist in the population, either by genetic or cultural inheritance. The first key concept in evolutionary game theory is ``evolutionary stable strategy" (ESS),  introduced in 1973, in the seminal paper of John Maynard Smith and George Price \cite{Maynard-Smith:Nature:1973}. A (monomorphic) population playing an ESS cannot be invaded by mutants. 
\noindent The concept of ``evolutionary stable strategy" (ESS), originally proposed for parwise encounters \cite{Maynard-Smith:Nature:1973}, was extended for multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}. Also the well-known replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}. More recently, the replicator-mutator equation was applied to study the dynamics of multiplayer games, too \cite{Duong:DGAA:2020}. 
As for asymmetric games, a few additional assumptions are needed. For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Gokhale:PRSB:2012, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}. For role games, a strategy must include the action played in each of the two roles. The case of asymmetric games with more than two players is substantially less studied within deterministic EGT. Gokhale and Traulsen (2012) and Zhang et al. (2022) are two exceptions \cite{Gokhale:PRSB:2012, Zhang:arxiv:2022}. Notably, although these works study multiplayer games, they consider, at most, two different types (drawn from two populations), which leaves out the exploration of full asymmetry.
% models of multiple populations seem unnatural
\\ \\
% stochastic EGT
\noindent Also stochastic evolutionary game dynamics \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009} provides several models for studying multiplayer and asymmetric games. 
%Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}. 
%These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. 
Fixation probabilities \cite{Fudenberg:TPB:2006} for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived. Furthermore, average strategy abundances \cite{antal:JTB:2009a, antal:JTB:2009b} were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}. For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to Gokhale and Traulsen (2014) \cite{Gokhale:DGAA:2014}.\\

%When deriving fixation probabilities and times, it is assumed that mutations are rare, such that, no new mutant arises between the very first and its eventual fixation \cite{}. 
%\cite{Chalub:BMB:2019}

%strategy abundance papers (intermediate mutation or mutation-selection equilibrium)
%2-player symmetric and asymmetric games, any number of strategies, Birth-death process \cite{ohtsuki:JTB:2010}
%2-player symmetric and asymmetric games, any number of strategies, Death-birth process \cite{Sekiguchi:PA:2013}

@@

%[Learning models]
%learning models in general
\noindent Learning models (of strategic behavior) take a different approach from EGT \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}. There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically. 
%Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}. 
% Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}. The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made. Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{Fudenberg:book:1998b}. In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
%learning models for asymmetric and multiplayer games? fictious play for multiplayer games \cite{fudenberg:book:1998b} 
%can we say most of learning models have no analytical or exact results?
\noindent Introspection dynamics has recently proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}. 
This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a random player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round. We describe the model formally in the next section. 
While in Couto et al. (2022) \cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.  Particularly, introspection dynamics allows a natural exploration of full asymmetry in many-player games compared to population models. For example, in imitation dynamics, one needs to specify who imitates who \cite{Vasconcelos:PNAS:2014}, as when players differ much, it might not make sense to assume they imitate any other player with the same likelihood. Introspection avoids this assumption because players' decisions only depend on their own payoffs.
\\ \\
%[Our proposal]
\noindent Here, we extend previous results of pairwise games under introspection dynamics to multiplayer games. 
First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
Second, we obtain explicit expressions of the stationary distribution for two special cases. These cases are additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and symmetric multiplayer games with two strategies. 
To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games. Finally, we also study the asymmetric version of a public goods game with a rewarding stage \cite{Pal:NatCom:2022}.

@@

\label{Th:additive-games-stationary-dist}
\end{Prop}
\noindent For a proof of the Propositions and Corollaries, please see Appendix. Using the stationary distribution and Eq. (\ref{Eq:marginal-definition}), one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distributions). In this regard, introspection learning in additive games is particularly interesting. The stationary distribution and the marginal distributions of introspection dynamics in additive games are related in a special way,

@@

\noindent For the $N$-player additive game, $\xi_{j,a_j}$ is given by,

@@

We also study introspection dynamics in this game with asymmetric players. We use the same setup that we used for studying the asymmetric linear public goods. The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2. In Supplementary Figure 1, we study two cases, first in which the public good is synergistic and players have a high average cost, and second in which public good is discounted and players have a lower average cost. In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit. The only noticebale difference between the two cases is the minimum relationship between the asymmetries $\delta_b$ and $\delta_c$ that results in high cooperation for the player with low cost and high benefit. When we observe individual cooperation frequency versus the synergy/discount factor, $w$ (Supplementary Figure 2), we find that when players are symmetric with respect to just benefits (or just costs), the one with the lowest cost (or highest benefit) cooperates with a high probability across all types of public goods, even for a high value of average cost.
